Preliminary (quick and dirty) results

### 2022-07-06 slides/results.Rmd
update fonts to google fonts from manual theme

```{r xaringan-themer, include=FALSE, warning=FALSE}
style_mono_accent(
  base_color = "#0046a6"
)
```

@@

```{r}
q_google_demos %>% 
  ggplot(aes(x = age, fill = gender)) +
  geom_histogram(position = "identity", alpha = 0.5, binwidth = 2) +
  scale_y_continuous(breaks = scales::breaks_extended(6))
```

@@

```{r}
retrieval %>%
  mutate(across(c(resp_pic, resp_source),
                ~if_else(. > 0, 1L, 0L))) %>% 
  group_by(subj_num, j_score) %>% 
  summarize(acc_pic = mean(resp_pic),
            acc_source = mean(resp_source)) %>% 
  pivot_longer(cols = starts_with("acc"),
               names_to = "memory_type",
               values_to = "acc",
               names_prefix = "acc_") %>% 
  ggplot(aes(x = j_score, y = acc, color = memory_type, fill = memory_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)") +
  theme_bw()
```

>>>>

```{r xaringan-themer, include=FALSE, warning=FALSE}
style_mono_accent(
  base_color = "#0046a6",
  text_font_google = google_font("Lora"),
  header_font_google = google_font("Nunito"),
  code_font_google = google_font("Fira Code")
)
```

@@

```{r}
q_google_demos %>% 
  left_join(q_google_demos %>%
              count(gender) %>%
              mutate(gender_n = glue::glue("{gender} (n = {n})")) %>%
              select(-n),
            by = "gender") %>% 
  ggplot(aes(x = age, fill = gender_n)) +
  geom_histogram(position = "identity", alpha = 0.5, binwidth = 2) +
  scale_y_continuous(breaks = scales::breaks_extended(6))
```

@@

```{r}
retrieval %>%
  # filter(already_knew == "none") %>% 
  mutate(across(c(resp_pic, resp_source),
                ~if_else(. > 0, 1L, 0L))) %>% 
  group_by(subj_num, j_score) %>% 
  summarize(acc_pic = mean(resp_pic),
            acc_source = mean(resp_source)) %>% 
  pivot_longer(cols = starts_with("acc"),
               names_to = "memory_type",
               values_to = "acc",
               names_prefix = "acc_") %>% 
  ggplot(aes(x = j_score, y = acc, color = memory_type, fill = memory_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)") +
  theme_bw()
```
